R Packages to Aid in Handling Web Access Logs

### 2016-01-01 paper/paper.Rmd
update to include latest iptools changes

\pkg{iptools} also contains (for the same purpose) code to identify the actual client's IP address. Access requests usually contain not only an IP address but a \dfn{X-Forwarded-For} field - a field identifying which \emph{other} IP addresses the request passed through, if the user who made the request is using some kind of proxy. If a user \emph{has} used a proxy, the contents of the IP address field won't actually be them - it will be the last proxy the request went through before getting to the server logging the requests. The actual IP address of the user will instead be the earliest value of the X-Forwarded-For field.

@@

The limitation of the package is that it does not yet work on Windows - building ASIO on that platform is a uniquely frustrating experience - and that some operations do not yet support IPv6 (since they require the storage of numbers bigger than R can currently handle).

>>>>

Along with this general tool there are also functions for ascertaining specific facts about IP addresses, returning logical (\code{TRUE} or \code{FALSE}) values. These are \code{is\_valid}, \code{is\_ipv4}, \code{is\_ipv6}, which are built on top of \code{ip\_classify}, and \code{is\_multicast}, which identifies if an IP address is \dfn{multicast} - designed to point to multiple machines.

\pkg{iptools} also contains (for similar purposes) code to identify the actual client's IP address. Access requests usually contain not only an IP address but a \dfn{X-Forwarded-For} field - a field identifying which \emph{other} IP addresses the request passed through, if the user who made the request is using some kind of proxy. If a user \emph{has} used a proxy, the contents of the IP address field won't actually be them - it will be the last proxy the request went through before getting to the server logging the requests. The actual IP address of the user will instead be the earliest value of the X-Forwarded-For field.

@@

The limitation of the package is that it some operations do not yet support IPv6 (since they require the storage of numbers bigger than R can currently handle).

### 2016-01-01 paper/paper.tex
update to include latest iptools changes

\abstract{%
Web access logs contain information on HTTP(S) requests and form a key
part of both industry and academic explorations of human behaviour on
the internet - explorations commonly performed in R. In this paper we
explain and demonstrate a series of packages designed to efficiently
read in, parse and munge access log data, allowing researchers to handle
it easily.
}

@@

\address{%
Oliver Keyes\\
Wikimedia Foundation\\
149 New Montgomery Street, 6th floor\\ San Francisco, CA, 94105, USA\\
}
\href{mailto:ironholds@gmail.com}{\nolinkurl{ironholds@gmail.com}}

\address{%
Bob Rudis\\
Rapid7\\
line 1\\ line 2\\
}
\href{mailto:author2@work}{\nolinkurl{author2@work}}

\address{%
Jay Jacobs\\
Magical Python Land\\
line 1\\ line 2\\
}
\href{mailto:author3@work}{\nolinkurl{author3@work}}

>>>>

\abstract{
Web access logs contain information on HTTP(S) requests and form a key
part of both industry and academic explorations of human behaviour on
the internet - explorations commonly performed in R. In this paper we
explain and demonstrate a series of packages designed to efficiently
read in, parse and munge access log data, allowing researchers to handle
it easily.
}

@@

\address{
Oliver Keyes\\
Wikimedia Foundation\\
149 New Montgomery Street, 6th floor\\ San Francisco, CA, 94105, USA\\
}
\href{mailto:ironholds@gmail.com}{\nolinkurl{ironholds@gmail.com}}

\address{
Bob Rudis\\
Rapid7\\
line 1\\ line 2\\
}
\href{mailto:author2@work}{\nolinkurl{author2@work}}

\address{
Jay Jacobs\\
Magical Python Land\\
line 1\\ line 2\\
}
\href{mailto:author3@work}{\nolinkurl{author3@work}}
